---
title: "Report 090821 female"
author: "Tom Mushkat"
date: "08/08/21"
output:
  html_document:
    code_folding: hide
    df_print: kable
    results: hide
    theme: readable
    toc: TRUE
    toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, warning=FALSE, message=FALSE}
pacman::p_load(tidyverse, here, anytime, car, effectsize, gmodels, apaTables, psych, rcompanion, ResourceSelection, lmtest, faraway, estimatr, tidymodels, hdm)

Data <- read_csv(here('Data/cleanDataUpdated.csv'))

Data$emCondition <- as.factor(Data$emCondition)

# Data$emCondition <- ordered(Data$emCondition, levels = c('No', 'Single', 'Many'))

Data <- Data %>% 
  filter(understandPurpse == 'didNotUnderstand')
# Data <- Data %>%
#   filter(mf == 'Female')
```







This is the distribution of the money that was sent to Player B.
We can see that this is a bi-modal distribution where some of the participants sent the max amount, and some, about 5 cents.

Therefore using K-Means method I split the data into two groups, and performed a logistic regression for predicting the new clusters using the emoji condition.

I also removed participants (N = 33) that by self report indicated that they understood the experiment when Player B sent the message.

```{r, warning=FALSE, message=FALSE}
hist(Data$Amount)
hist(Data$Trust)
```

Using K-Means model I classified the money variable into two groups (Means of 4.70 and 9.82)

```{r, warning=FALSE, message=FALSE}
set.seed(1)
Model <- kmeans(x = Data$Amount, centers = 2)
Model
Data$clusters <- Model$cluster
Data$clusters <- ifelse(Data$clusters == 2, 'Sent a little', 'Sent a lot')
table(Data$clusters)
Data$clusters <- ifelse(Data$clusters == 'Sent a lot', 1, 0)
Data$clusters <- as.factor(Data$clusters)


set.seed(1)
Model <- kmeans(x = Data$Trust, centers = 3)
Model
Data$clustersTrust <- Model$cluster
Data$clustersTrust <- ifelse(Data$clustersTrust == 2, 3,
                             ifelse(Data$clustersTrust == 1, 2, 1))
table(Data$clustersTrust)
# Data$clusters <- ifelse(Data$clusters == 'Sent a lot', 1, 0)
Data$clustersTrust <- as.factor(Data$clustersTrust)
```



```{r, warning=FALSE, message=FALSE}
# Data %>% 
#   group_by(emCondition, clustersTrust) %>%
#   summarise(Trust = length(clustersTrust) / nrow(Data)) %>%
#   mutate(emCondition = ordered(emCondition, levels = c('No', 'Single', 'Many'))) %>% 
#   ggplot(aes(x = emCondition, y = Trust)) +
#   geom_bar(stat = 'identity') +
#   scale_y_continuous(labels=scales::percent)
# 
# Data %>% 
#   # group_by(emCondition, mf) %>% 
#   # summarise(Trust = length(clustersTrust) / nrow(Data)) %>% 
#   mutate(emCondition = ordered(emCondition, levels = c('No', 'Single', 'Many'))) %>% 
#   ggplot(aes(x = emCondition, y = clustersTrust)) +
#   geom_bar(aes(y = (..count..) / sum(..count..))) +
#   scale_y_continuous(labels=scales::percent)
# 
# Data %>% 
#   # group_by(emCondition, mf) %>% 
#   # summarise(Trust = length(clustersTrust) / nrow(Data)) %>% 
#   mutate(emCondition = ordered(emCondition, levels = c('No', 'Single', 'Many'))) %>% 
#   ggplot(aes(x = emCondition, y = clustersTrust)) +
#   geom_bar(aes(y = (..count..) / sum(..count..))) +
#   scale_y_continuous(labels=scales::percent) +
#   facet_grid(~mf)

# Trust: 1 = Little, 2 == Medium, 3 == High

Data %>% 
  group_by(emCondition, mf) %>%
  summarise(Trust = length(clustersTrust)) %>%
  # mutate(emCondition = ordered(emCondition, levels = c('No', 'Single', 'Many'))) %>%
  ggplot(aes(x = emCondition, y = Trust)) +
  geom_bar(stat = 'identity') +
  # scale_y_continuous(labels=scales::percent) 
  facet_grid(~Trust)

# Data %>% 
#   group_by(emCondition, mf) %>%
#   summarise(Trust = length(clustersTrust) / nrow(Data)) %>%
#   mutate(emCondition = ordered(emCondition, levels = c('No', 'Single', 'Many'))) %>%
#   ggplot(aes(x = emCondition, y = clustersTrust)) +
#   geom_bar(aes(y = (..count..) / sum(..count..))) +
#   scale_y_continuous(labels=scales::percent) +
#   facet_grid(~clustersTrust)
CrossTable(Data$emCondition, Data$clustersTrust, chisq = T, format = 'SPSS')


Data %>% 
  # group_by(emCondition, mf) %>% 
  # summarise(Trust = length(clustersTrust) / nrow(Data)) %>% 
  # mutate(emCondition = ordered(emCondition, levels = c('No', 'Single', 'Many'))) %>% 
  ggplot(aes(x = emCondition, y = clustersTrust)) +
  geom_bar(aes(y = (..count..) / sum(..count..))) +
  scale_y_continuous(labels=scales::percent) +
  facet_grid(~mf * clustersTrust)
CrossTable(Data$emCondition[Data$mf == 'Male'], Data$clustersTrust[Data$mf == 'Male'], chisq = T, format = 'SPSS')
CrossTable(Data$emCondition[Data$mf == 'Female'], Data$clustersTrust[Data$mf == 'Female'], chisq = T, format = 'SPSS')

# Money: 0 == Little (~5), 1 == High (~10)

Data %>% 
  # group_by(emCondition, mf) %>% 
  # summarise(Trust = length(clustersTrust) / nrow(Data)) %>% 
  # mutate(emCondition = ordered(emCondition, levels = c('No', 'Single', 'Many'))) %>% 
  ggplot(aes(x = emCondition, y = clusters)) +
  geom_bar(aes(y = (..count..) / sum(..count..))) +
  scale_y_continuous(labels=scales::percent) +
  facet_grid(~clusters)
CrossTable(Data$emCondition, Data$clusters, chisq = T, format = 'SPSS')

Data %>% 
  # group_by(emCondition, mf) %>% 
  # summarise(Trust = length(clustersTrust) / nrow(Data)) %>% 
  # mutate(emCondition = ordered(emCondition, levels = c('No', 'Single', 'Many'))) %>% 
  ggplot(aes(x = emCondition, y = clusters)) +
  geom_bar(aes(y = (..count..) / sum(..count..))) +
  scale_y_continuous(labels=scales::percent) +
  facet_grid(~mf * clusters)
CrossTable(Data$emCondition[Data$mf == 'Male'], Data$clusters[Data$mf == 'Male'], chisq = T, format = 'SPSS')
CrossTable(Data$emCondition[Data$mf == 'Female'], Data$clusters[Data$mf == 'Female'], chisq = T, format = 'SPSS')

```


```{r, warning=FALSE, message=FALSE}
library(nnet)
Data$emCondition <- as.factor(ifelse(Data$emCondition == 'No', 1,
                                     ifelse(Data$emCondition == 'Single', 2, 3)))
levels(Data$clustersTrust)
levels(Data$emCondition)
No <- c(1, 0, 0)
Single <- c(0, 1, 0)
Many <- c(0, 0, 1)
contrasts(Data$emCondition) <- cbind(Single, Many)



test <- multinom(clustersTrust ~ emCondition + mf, data = Data)
summary(test)

z <- summary(test)$coefficients/summary(test)$standard.errors
z

p <- (1 - pnorm(abs(z), 0, 1)) * 2
p
```


# Univariate correlation
## Chi-square table (1 == sending large amount of money)

The univariate correlation between the emoji condition and DV was conducted using Chi-Square.
The results show no significant correlation between the conditions $(X^2(2) = 3.94, p = .14)$. However, we can see that the participants in the single condition (64.29%) sent higher amount of money in comparison with the other conditions (No EM = 55.43%; Multiple EM = 48.61%).

```{r, warning=FALSE, message=FALSE}
CrossTable(Data$clusters, Data$emCondition, chisq = T, format = 'SPSS')
```

# Multivaraite correlations
## Regressions weights: comparing the emoji groups to the no emoji group (No effects)

```{r, warning=FALSE, message=FALSE}
Data$emCondition <- as.factor(Data$emCondition)
contrasts(Data$emCondition)
No <- c(0, 1, 0)
Single <- c(0, 0, 1)
Many <- c(1, 0, 0)
contrasts(Data$emCondition) <- cbind(Single, Many)
contrasts(Data$emCondition)
```

### Amount
A logistic regression model was conducted for predicting the probability to send higher amount of money. The model was conducted while controlling the participants' gender.

The model was significant $(X^2(3) = 7.97, p = .046)$ while explaining 4.24% of the total variance in the amount of money that was sent to Player B.
The model is well-fit to data $(X^2(8) = 2.72, p = .95)$ while classifying about 58.87% of total observations, with sensitivity of 29.45% and specificity of 73.57%.

After controlling the participants' gender, the model showed no significant correlations between the emoji conditions and the probability to send a large amount of money.

**The model's summary and the Odds ratio with the CI are presented below.**

```{r, warning=FALSE, message=FALSE}
regLog1 <- glm(clusters ~ emCondition, family = binomial('logit'), data = Data)
summary(regLog1)
```

**Odds ratio**
```{r, warning=FALSE, message=FALSE}
ORCI <- round(exp(cbind(coef(regLog1), confint(regLog1))), 2) 
ORCI
```

### Trust
Linear regression was performed for predicting the Trust in Player B.
The regression was performed while controlling gender, religiously, Motives, Attitudes, emoji Use and how much they were positively/negatively influenced by Player's B message (No multicollinearity was found).

The model was significant $(F(8) = 7.04, p < .01)$ while explaining 16.37% of the total variance in the Trust in Player B.

After controlling the control variables, there was found no correlations between the emoji condition and the DV.

**The model's summary and standardized beta coefficients are presented below.**

```{r, warning=FALSE, message=FALSE}
Model <- lm(Trust ~ emConditionNo+ Secular + Motives + Attitudes + emojiUse + influencedFactors, data = Data) 
# vif(Model)
varTest <- bptest(Model)    # lmtest package
regType <- ifelse(varTest$p.value < 0.05, 'HC2', 'classical')

Model <- lm_robust(Trust ~ emConditionNo + mf + Secular + Motives + Attitudes + emojiUse + influencedFactors, se_type =  regType, data = Data)
scalednewData <- Data %>% 
  mutate(Motives = scale(Motives),
         Attitudes = scale(Attitudes),
         emojiUse = scale(emojiUse),
         Trust = scale(Trust))

Model1 <- lm_robust(Trust ~ emConditionNo + mf + Secular + Motives + Attitudes + emojiUse + influencedFactors, se_type = regType, data = scalednewData)
summary(Model)
```

**Standardized beta coefficients** 
```{r, warning=FALSE, message=FALSE}
round(Model1$coefficients, 2)
```

## Regression weights: comparing the Single emoji group to the no and multiple emoji groups

```{r, warning=FALSE, message=FALSE}
Data$emConditionSingle <- Data$emCondition
# contrasts(Data$emConditionSingle)
No <- c(1, 0, 0)
Many <- c(0, 0, 1)
contrasts(Data$emConditionSingle) <- cbind(No, Many)
contrasts(Data$emConditionSingle)
```

### Amount

A logistic regression model was conducted for predicting the probability to send higher amount of money. The model was conducted while controlling the participants' gender.

The model was significant $(X^2(3) = 7.97, p = .046)$ while explaining 4.24% of the total variance in the amount of money that was sent to Player B.
The model is well-fit to data $(X^2(8) = 2.72, p = .95)$ while classifying about 58.87% of total observations, with sensitivity of 29.45% and specificity of 73.57%.

After controlling the participants' gender and perceived influence, the model showed a weak but significant negative correlation between the multiple emoji condition and the probability to send a large amount of money $(OR = 0.52, CI[0.27, 0.99], p = .047)$. Meaning, receiving a message with multiple emojis, in comparison with a single emoji, decreases the probability to send a large amount of money. 

**The model's summary and the Odds ratio with the CI are presented below.**

```{r, warning=FALSE, message=FALSE}
regLog1 <- glm(clusters ~ emConditionSingle, family = binomial('logit'), data = Data)
summary(regLog1)
```

**Odds ratio**
```{r, warning=FALSE, message=FALSE}
ORCI <- round(exp(cbind(coef(regLog1), confint(regLog1))), 2) 
ORCI
```

### Trust
Linear regression was performed for predicting the Trust in Player B.
The regression was performed while controlling gender, religiously, Motives, Attitudes, emoji Use and how much they were positively/negatively influenced by Player's B message (No multicollinearity was found).

The model was significant $(F(8) = 7.04, p < .01)$ while explaining 16.37% of the total variance in the Trust in Player B.

After controlling the control variables, there was found no correlations between the emoji condition and the DV.

**The model's summary and standardized beta coefficients are presented below.**

```{r, warning=FALSE, message=FALSE}
Model <- lm(Trust ~ emConditionSingle + mf + Secular + Motives + Attitudes + emojiUse + influencedFactors, data = Data) 
# vif(Model)
varTest <- bptest(Model)    # lmtest package
regType <- ifelse(varTest$p.value < 0.05, 'HC2', 'classical')

Model <- lm_robust(Trust ~ emConditionSingle + mf + Secular + Motives + Attitudes + emojiUse + influencedFactors, se_type =  regType, data = Data)
scalednewData <- Data %>% 
  mutate(Motives = scale(Motives),
         Attitudes = scale(Attitudes),
         emojiUse = scale(emojiUse),
         Trust = scale(Trust))

Model1 <- lm_robust(Trust ~ emConditionSingle + mf + Secular + Motives + Attitudes + emojiUse + influencedFactors, se_type = regType, data = scalednewData)
summary(Model)
```

**Standardized beta coefficients** 
```{r, warning=FALSE, message=FALSE}
round(Model1$coefficients, 2)
```
