---
title: "Demographic characteristics"
author: "Tom Mushkat"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    code_folding: hide
    df_print: kable
    results: hide
    theme: readable
    toc: TRUE
    toc_float: TRUE
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Age
## Descriptive statistics
```{r, warning=FALSE, message=FALSE}
table(Data$howDecide)
table(Data$howDecide, Data$Order)
table(Data$howDecide, Data$emCondition)


skim(Data$Age)
```

## Correlations with Order
```{r, warning=FALSE, message=FALSE}
Data %>% 
  group_by(Order) %>% 
  summarise(Mean = round(mean(Age), 2),
            SD   = round(sd(Age), 2))

varTest <- var.test(Age ~ Order, data = Data)
trueVarTest <- ifelse(varTest$p.value > 0.05, TRUE, FALSE)
Model <- t.test(Age ~ Order, var.equal = trueVarTest, data = Data)
Model
effectsize(Model)

boxplot(Data$Age ~ Data$Order,
  ylab = "Age",
  main = 'Order'
)
```

## Correlations with emCondition
```{r, warning=FALSE, message=FALSE}
Data %>% 
  group_by(emCondition) %>% 
  summarise(Mean = round(mean(Age), 2),
            SD   = round(sd(Age), 2))

Leven <- leveneTest(Data$Age ~ Data$emCondition)  # car packages
trueVarTest <- ifelse(varTest$p.value < 0.05, TRUE, FALSE)
Model <- aov(Age ~ emCondition, data = Data)
Anova(Model, type = 'III', white.adjust = trueVarTest)
```

```{r, warning=FALSE, message=FALSE}
corData <- Data %>% 
  select(Age, Amount, Trust)
apa.cor.table(corData)
```



# Gender
## Descriptive statistics
```{r, warning=FALSE, message=FALSE}
table(Data$Gender)
round(100 * table(Data$Gender) / nrow(Data), 2)

table(Data$mf)
round(100 * table(Data$mf) / nrow(Data), 2)
```

## Correlations with emCondition
```{r, warning=FALSE, message=FALSE}
CrossTable(Data$mf, Data$emCondition, format = 'SPSS', chisq = T)
```

## Correlations with Order
```{r, warning=FALSE, message=FALSE}
CrossTable(Data$mf, Data$Order, format = 'SPSS', chisq = T)
```

## Correlations with Amount
```{r, warning=FALSE, message=FALSE}
Data %>% 
  group_by(mf) %>% 
  summarise(Mean = round(mean(Amount), 2),
            SD   = round(sd(Amount), 2))

varTest <- var.test(Amount ~ mf, data = Data)
trueVarTest <- ifelse(varTest$p.value > 0.05, TRUE, FALSE)
Model <- t.test(Amount ~ mf, var.equal = trueVarTest, data = Data)
Model

effectsize(Model)

boxplot(Data$Amount ~ Data$mf,
  ylab = "Amount",
  main = 'Gender'
)

```

## Correlations with Trust
```{r, warning=FALSE, message=FALSE}
Data %>% 
  group_by(mf) %>% 
  summarise(Mean = round(mean(Trust), 2),
            SD   = round(sd(Trust), 2))

varTest <- var.test(Trust ~ mf, data = Data)
trueVarTest <- ifelse(varTest$p.value > 0.05, TRUE, FALSE)
Model <- t.test(Trust ~ mf, var.equal = trueVarTest, data = Data)
Model

effectsize(Model)

boxplot(Data$Trust ~ Data$mf,
  ylab = "Trust",
  main = 'Gender'
)
```

# maritalStatus
## Descriptive statistics
```{r, warning=FALSE, message=FALSE}
table(Data$maritalStatus)
round(100 * table(Data$maritalStatus) / nrow(Data), 2)

Data <- Data %>% 
  mutate(originalMaritalStatus = maritalStatus,
         maritalStatus = ifelse(maritalStatus == 'Married' | maritalStatus == 'In a serious relationship', 'Married', 'nonMarreid'))

```

## Correlations with emCondition
```{r, warning=FALSE, message=FALSE}
CrossTable(Data$maritalStatus, Data$emCondition, format = 'SPSS', chisq = T)
```

## Correlations with Order
```{r, warning=FALSE, message=FALSE}
CrossTable(Data$maritalStatus, Data$Order, format = 'SPSS', chisq = T)
```

## Correlations with Amount
```{r, warning=FALSE, message=FALSE}
Data %>% 
  group_by(maritalStatus) %>% 
  summarise(Mean = round(mean(Amount), 2),
            SD   = round(sd(Amount), 2))

varTest <- var.test(Trust ~ maritalStatus, data = Data)
trueVarTest <- ifelse(varTest$p.value > 0.05, TRUE, FALSE)
Model <- t.test(Trust ~ maritalStatus, var.equal = trueVarTest, data = Data)
Model
```

## Correlations with Trust
```{r, warning=FALSE, message=FALSE}
Data %>% 
  group_by(maritalStatus) %>% 
  summarise(Mean = round(mean(Trust), 2),
            SD   = round(sd(Trust), 2))

varTest <- var.test(Trust ~ maritalStatus, data = Data)
trueVarTest <- ifelse(varTest$p.value > 0.05, TRUE, FALSE)
Model <- t.test(Trust ~ maritalStatus, var.equal = trueVarTest, data = Data)
Model
```

# Parent
## Descriptive statistics
```{r, warning=FALSE, message=FALSE}
table(Data$Parent)
round(100 * table(Data$Parent) / nrow(Data), 2)
```

## Correlations with emCondition
```{r, warning=FALSE, message=FALSE}
CrossTable(Data$Parent, Data$emCondition, format = 'SPSS', chisq = T)
```

## Correlations with Order
```{r, warning=FALSE, message=FALSE}
CrossTable(Data$Parent, Data$Order, format = 'SPSS', chisq = T)
```

## Correlations with Trust
```{r, warning=FALSE, message=FALSE}
Data %>% 
  group_by(Parent) %>% 
  summarise(Mean = round(mean(Amount), 2),
            SD   = round(sd(Amount), 2))

varTest <- var.test(Amount ~ Parent, data = Data)
trueVarTest <- ifelse(varTest$p.value > 0.05, TRUE, FALSE)
Model <- t.test(Amount ~ Parent, var.equal = trueVarTest, data = Data)
Model
```

## Correlations with Trust
```{r, warning=FALSE, message=FALSE}
Data %>% 
  group_by(Parent) %>% 
  summarise(Mean = round(mean(Trust), 2),
            SD   = round(sd(Trust), 2))

varTest <- var.test(Trust ~ Parent, data = Data)
trueVarTest <- ifelse(varTest$p.value > 0.05, TRUE, FALSE)
Model <- t.test(Trust ~ Parent, var.equal = trueVarTest, data = Data)
Model
```

# Religion
## Descriptive statistics
```{r, warning=FALSE, message=FALSE}
table(Data$originalReligion)

CrossTable(Data$Religion, Data$religionAffiliation, chisq = T, format = 'SPSS')
round(100 * table(Data$Religion) / nrow(Data), 2)

Data <- Data %>% 
  mutate(originalReligion = Religion,
         Religion = ifelse(Religion == 'Christian', 'Christian', 'Other'))
```

## Correlations with emCondition
```{r, warning=FALSE, message=FALSE}
CrossTable(Data$Religion, Data$emCondition, format = 'SPSS', chisq = T)
```

## Correlations with Order
```{r, warning=FALSE, message=FALSE}
CrossTable(Data$Religion, Data$Order, format = 'SPSS', chisq = T)
```

## Correlations with Amount
```{r, warning=FALSE, message=FALSE}
Data %>% 
  group_by(Religion) %>% 
  summarise(Mean = round(mean(Amount), 2),
            SD   = round(sd(Amount), 2))

varTest <- var.test(Amount ~ Religion, data = Data)
trueVarTest <- ifelse(varTest$p.value > 0.05, TRUE, FALSE)
Model <- t.test(Amount ~ Religion, var.equal = trueVarTest, data = Data)
Model
```

## Correlations with Trust
```{r, warning=FALSE, message=FALSE}
Data %>% 
  group_by(Religion) %>% 
  summarise(Mean = round(mean(Trust), 2),
            SD   = round(sd(Trust), 2))

varTest <- var.test(Trust ~ Religion, data = Data)
trueVarTest <- ifelse(varTest$p.value > 0.05, TRUE, FALSE)
Model <- t.test(Trust ~ Religion, var.equal = trueVarTest, data = Data)
Model

effectsize(Model)

boxplot(Data$Trust ~ Data$Religion,
  ylab = "Trust",
  main = 'Religion'
)
```

# religionAffiliation
## Descriptive statistics
```{r, warning=FALSE, message=FALSE}
table(Data$religionAffiliation)
round(100 * table(Data$religionAffilation) / nrow(Data), 2)

Data$Secular <- ifelse(Data$religionAffiliation == 'Secular', 'Secular', 'nonSecular')
```

## Correlations with emCondition
```{r, warning=FALSE, message=FALSE}
CrossTable(Data$Secular, Data$emCondition, format = 'SPSS', chisq = T)
```

## Correlations with Order
```{r, warning=FALSE, message=FALSE}
CrossTable(Data$Secular, Data$Order, format = 'SPSS', chisq = T)
```

## Correlations with Amount
```{r, warning=FALSE, message=FALSE}
Data %>% 
  group_by(Secular) %>% 
  summarise(Mean = round(mean(Amount), 2),
            SD   = round(sd(Amount), 2))

varTest <- var.test(Trust ~ Secular, data = Data)
trueVarTest <- ifelse(varTest$p.value > 0.05, TRUE, FALSE)
Model <- t.test(Trust ~ Secular, var.equal = trueVarTest, data = Data)
Model

effectsize(Model)

boxplot(Data$Trust ~ Data$Secular,
  ylab = "Trust",
  main = 'Secular'
)
```

## Correlations with Trust
```{r, warning=FALSE, message=FALSE}
Data %>% 
  group_by(Secular) %>% 
  summarise(Mean = round(mean(Trust), 2),
            SD   = round(sd(Trust), 2))

varTest <- var.test(Trust ~ Secular, data = Data)
trueVarTest <- ifelse(varTest$p.value > 0.05, TRUE, FALSE)
Model <- t.test(Trust ~ Secular, var.equal = trueVarTest, data = Data)
Model

effectsize(Model)

boxplot(Data$Trust ~ Data$Secular,
  ylab = "Trust",
  main = 'Secular'
)
```


# Education
## Descriptive statistics
```{r, warning=FALSE, message=FALSE}
table(Data$Education)
round(100 * table(Data$Education) / nrow(Data), 2)


Data <- Data %>% 
  mutate(originalEducation = Education,
         Education = ifelse(Education == 'High school graduate' | Education == 'Less than high school', 'Some college +', Education))

```

## Correlations with emCondition
```{r, warning=FALSE, message=FALSE}
CrossTable(Data$Education, Data$emCondition, format = 'SPSS', chisq = T)
```

## Correlations with Order
```{r, warning=FALSE, message=FALSE}
CrossTable(Data$Education, Data$Order, format = 'SPSS', chisq = T)
```

## Correlations with Amount
```{r, warning=FALSE, message=FALSE}
Data %>% 
  group_by(Education) %>% 
  summarise(Mean = round(mean(Amount), 2),
            SD   = round(sd(Amount), 2))

Leven <- leveneTest(Data$Amount ~ Data$Education)  # car packages
trueVarTest <- ifelse(varTest$p.value > 0.05, TRUE, FALSE)
Model <- aov(Amount ~ Education, var.equal = trueVarTest, data = Data)
Anova(Model, type = 'III', white.adjust = trueVarTest)
```

## Correlations with Trust
```{r, warning=FALSE, message=FALSE}
Data %>% 
  group_by(Education) %>% 
  summarise(Mean = round(mean(Trust), 2),
            SD   = round(sd(Trust), 2))

Leven <- leveneTest(Data$Trust ~ Data$Education)  # car packages
trueVarTest <- ifelse(varTest$p.value > 0.05, TRUE, FALSE)
Model <- aov(Trust ~ Education, var.equal = trueVarTest, data = Data)
Anova(Model, type = 'III', white.adjust = trueVarTest)
```


# Socioeconomic
## Descriptive statistics
```{r, warning=FALSE, message=FALSE}
table(Data$originalSocioeconomic)
round(100 * table(Data$Socioeconomic) / nrow(Data), 2)

Data <- Data %>% 
  mutate(originalSocioeconomic = Socioeconomic,
         Socioeconomic = ifelse(Socioeconomic == 'Less than $20,000' | Socioeconomic == '$20,000 - $39,999', 'Less then $39999',
                                ifelse(Socioeconomic == '$80,000 - $99,999' | Socioeconomic == '$100,000 - $119,999', '80000 - 119000', Socioeconomic)))
Data$Socioeconomic <- as.factor(Data$Socioeconomic)
levels(Data$Socioeconomic) <- c('Less then $39999', '$40,000 - $59,999', '$60,000 - $79,999', '80000 - 119000', '$120,000 or more')


```

## Correlations with emCondition
```{r, warning=FALSE, message=FALSE}
CrossTable(Data$Socioeconomic, Data$emCondition, format = 'SPSS', chisq = T)
```

## Correlations with Order
```{r, warning=FALSE, message=FALSE}
CrossTable(Data$Socioeconomic, Data$Order, format = 'SPSS', chisq = T)
```

## Correlations with Amount
```{r, warning=FALSE, message=FALSE}
Data %>% 
  group_by(Socioeconomic) %>% 
  summarise(Mean = round(mean(Amount), 2),
            SD   = round(sd(Amount), 2))

Leven <- leveneTest(Data$Amount ~ Data$Socioeconomic)  # car packages
trueVarTest <- ifelse(varTest$p.value > 0.05, TRUE, FALSE)
Model <- aov(Amount ~ Socioeconomic, var.equal = trueVarTest, data = Data)
Anova(Model, type = 'III', white.adjust = trueVarTest)
```

## Correlations with Trust
```{r, warning=FALSE, message=FALSE}
Data %>% 
  group_by(Socioeconomic) %>% 
  summarise(Mean = round(mean(Trust), 2),
            SD   = round(sd(Trust), 2))

Leven <- leveneTest(Data$Trust ~ Data$Socioeconomic)  # car packages
trueVarTest <- ifelse(varTest$p.value > 0.05, TRUE, FALSE)
Model <- aov(Trust ~ Socioeconomic, var.equal = trueVarTest, data = Data)
Anova(Model, type = 'III', white.adjust = trueVarTest)
```

# Political
## Descriptive statistics
```{r, warning=FALSE, message=FALSE}
table(Data$Politics)
round(100 * table(Data$Politics) / nrow(Data), 2)
```

## Correlations with emCondition
```{r, warning=FALSE, message=FALSE}
CrossTable(Data$Politics, Data$emCondition, format = 'SPSS', chisq = T)
```

## Correlations with Order
```{r, warning=FALSE, message=FALSE}
CrossTable(Data$Politics, Data$Order, format = 'SPSS', chisq = T)
```

## Correlations with Amount
```{r, warning=FALSE, message=FALSE}
Data %>% 
  group_by(Politics) %>% 
  summarise(Mean = round(mean(Amount), 2),
            SD   = round(sd(Amount), 2))

Leven <- leveneTest(Data$Amount ~ Data$Politics)  # car packages
trueVarTest <- ifelse(varTest$p.value > 0.05, TRUE, FALSE)
Model <- aov(Amount ~ Politics, var.equal = trueVarTest, data = Data)
Anova(Model, type = 'III', white.adjust = trueVarTest)
```

## Correlations with Trust
```{r, warning=FALSE, message=FALSE}
Data %>% 
  group_by(Politics) %>% 
  summarise(Mean = round(mean(Trust), 2),
            SD   = round(sd(Trust), 2))

Leven <- leveneTest(Data$Trust ~ Data$Politics)  # car packages
trueVarTest <- ifelse(varTest$p.value > 0.05, TRUE, FALSE)
Model <- aov(Trust ~ Politics, var.equal = trueVarTest, data = Data)
Anova(Model, type = 'III', white.adjust = trueVarTest)
```

# How decided
## Descriptive statistics
```{r, warning=FALSE, message=FALSE}
table(Data$howDecide)
round(100 * table(Data$Politics) / nrow(Data), 2)
```

## Correlations with emCondition
```{r, warning=FALSE, message=FALSE}
CrossTable(Data$influencedByB, Data$emCondition, format = 'SPSS', chisq = T)
```

## Correlations with Order
```{r, warning=FALSE, message=FALSE}
CrossTable(Data$influencedByB, Data$Order, format = 'SPSS', chisq = T)
```

## Correlations with Amount
```{r, warning=FALSE, message=FALSE}
Data %>% 
  group_by(influencedByB) %>% 
  summarise(Mean = round(mean(Amount), 2),
            SD   = round(sd(Amount), 2))

varTest <- var.test(Amount ~ influencedByB, data = Data)
trueVarTest <- ifelse(varTest$p.value > 0.05, TRUE, FALSE)
Model <- t.test(Amount ~ influencedByB, var.equal = trueVarTest, data = Data)
Model

effectsize(Model)

boxplot(Data$Amount ~ Data$influencedByB,
  ylab = "Amount",
  main = 'influencedByB'
)
```

## Correlations with Trust
```{r, warning=FALSE, message=FALSE}
Data %>% 
  group_by(influencedByB) %>% 
  summarise(Mean = round(mean(Trust), 2),
            SD   = round(sd(Trust), 2))

varTest <- var.test(Trust ~ influencedByB, data = Data)
trueVarTest <- ifelse(varTest$p.value > 0.05, TRUE, FALSE)
Model <- t.test(Trust ~ influencedByB, var.equal = trueVarTest, data = Data)
Model

effectsize(Model)

boxplot(Data$Trust ~ Data$influencedByB,
  ylab = "Trust",
  main = 'influencedByB'
)
```

## Correlations with Amount
```{r, warning=FALSE, message=FALSE}
table(Data$influencedByB, Data$understandPurpse)

Data %>% 
  group_by(Politics) %>% 
  summarise(Mean = round(mean(Amount), 2),
            SD   = round(sd(Amount), 2))

Leven <- leveneTest(Data$Amount ~ Data$influencedByB * Data$understandPurpse)  # car packages
trueVarTest <- ifelse(varTest$p.value < 0.05, TRUE, FALSE)
Model <- aov(Amount ~ Data$influencedByB * Data$understandPurpse, var.equal = trueVarTest, data = Data)
Anova(Model, type = 'III', white.adjust = trueVarTest)
```

## Correlations with Trust
```{r, warning=FALSE, message=FALSE}
Data %>% 
  group_by(Politics) %>% 
  summarise(Mean = round(mean(Trust), 2),
            SD   = round(sd(Trust), 2))

Leven <- leveneTest(Data$Trust ~ Data$Politics)  # car packages
trueVarTest <- ifelse(varTest$p.value > 0.05, TRUE, FALSE)
Model <- aov(Trust ~ Politics, var.equal = trueVarTest, data = Data)
Anova(Model, type = 'III', white.adjust = trueVarTest)
```
