---
title: "Demographic characteristics"
author: "Tom Mushkat"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    code_folding: hide
    df_print: kable
    results: hide
    theme: readable
    toc: TRUE
    toc_float: TRUE
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Age
## Descriptive statistics
```{r, warning=FALSE, message=FALSE}
skim(Data$Age)
```

## Correlations with Order
```{r, warning=FALSE, message=FALSE}
Data %>% 
  group_by(Order) %>% 
  summarise(Mean = round(mean(Age), 2),
            SD   = round(sd(Age), 2))

varTest <- var.test(Age ~ Order, data = Data)
trueVarTest <- ifelse(varTest$p.value > 0.05, TRUE, FALSE)
Model <- t.test(Age ~ Order, var.equal = trueVarTest, data = Data)
Model
```

## Correlations with emCondition
```{r, warning=FALSE, message=FALSE}
Data %>% 
  group_by(emCondition) %>% 
  summarise(Mean = round(mean(Age), 2),
            SD   = round(sd(Age), 2))

Leven <- leveneTest(Data$Age ~ Data$emCondition)  # car packages
trueVarTest <- ifelse(varTest$p.value > 0.05, TRUE, FALSE)
Model <- aov(Age ~ emCondition, var.equal = trueVarTest, data = Data)
Anova(Model, type = 'III', white.adjust = trueVarTest)
```

```{r, warning=FALSE, message=FALSE}
corData <- Data %>% 
  select(Age, Amount, Trust)
apa.cor.table(corData)
```



# Gender
## Descriptive statistics
```{r, warning=FALSE, message=FALSE}
table(Data$Gender)
round(100 * table(Data$Gender) / nrow(Data), 2)
```

## Correlations with emCondition
```{r, warning=FALSE, message=FALSE}
CrossTable(Data$Gender[Data$Gender != 'Other'], Data$emCondition[Data$Gender != 'Other'], format = 'SPSS', chisq = T)
```

## Correlations with Order
```{r, warning=FALSE, message=FALSE}
CrossTable(Data$Gender[Data$Gender != 'Other'], Data$Order[Data$Gender != 'Other'], format = 'SPSS', chisq = T)
```

## Correlations with Amount
```{r, warning=FALSE, message=FALSE}
Data %>% 
  filter(Gender != 'Other') %>% 
  group_by(Gender) %>% 
  summarise(Mean = round(mean(Amount), 2),
            SD   = round(sd(Amount), 2))

varTest <- var.test(Amount ~ Gender, data = Data[Data$Gender != 'Other', ])
trueVarTest <- ifelse(varTest$p.value > 0.05, TRUE, FALSE)
Model <- t.test(Amount ~ Gender, var.equal = trueVarTest, data = Data[Data$Gender != 'Other', ])
Model
```

## Correlations with Trust
```{r, warning=FALSE, message=FALSE}
Data %>% 
  filter(Gender != 'Other') %>% 
  group_by(Gender) %>% 
  summarise(Mean = round(mean(Trust), 2),
            SD   = round(sd(Trust), 2))

varTest <- var.test(Trust ~ Gender, data = Data[Data$Gender != 'Other', ])
trueVarTest <- ifelse(varTest$p.value > 0.05, TRUE, FALSE)
Model <- t.test(Trust ~ Gender, var.equal = trueVarTest, data = Data[Data$Gender != 'Other', ])
Model
```

# maritalStatus
## Descriptive statistics
```{r, warning=FALSE, message=FALSE}
table(Data$maritalStatus)
round(100 * table(Data$maritalStatus) / nrow(Data), 2)
```

## Correlations with emCondition
```{r, warning=FALSE, message=FALSE}
CrossTable(Data$maritalStatus, Data$emCondition, format = 'SPSS', chisq = T)
```

## Correlations with Order
```{r, warning=FALSE, message=FALSE}
CrossTable(Data$maritalStatus, Data$Order, format = 'SPSS', chisq = T)
```

## Correlations with Amount
```{r, warning=FALSE, message=FALSE}
Data %>% 
  group_by(maritalStatus) %>% 
  summarise(Mean = round(mean(Amount), 2),
            SD   = round(sd(Amount), 2))

Leven <- leveneTest(Data$Amount ~ Data$maritalStatus)  # car packages
trueVarTest <- ifelse(varTest$p.value > 0.05, TRUE, FALSE)
Model <- aov(Amount ~ maritalStatus, var.equal = trueVarTest, data = Data)
Anova(Model, type = 'III', white.adjust = trueVarTest)
```

## Correlations with Trust
```{r, warning=FALSE, message=FALSE}
Data %>% 
  group_by(maritalStatus) %>% 
  summarise(Mean = round(mean(Trust), 2),
            SD   = round(sd(Trust), 2))

Leven <- leveneTest(Data$Trust ~ Data$maritalStatus)  # car packages
trueVarTest <- ifelse(varTest$p.value > 0.05, TRUE, FALSE)
Model <- aov(Trust ~ maritalStatus, var.equal = trueVarTest, data = Data)
Anova(Model, type = 'III', white.adjust = trueVarTest)
```

# Parent
## Descriptive statistics
```{r, warning=FALSE, message=FALSE}
table(Data$Parent)
round(100 * table(Data$Parent) / nrow(Data), 2)
```

## Correlations with emCondition
```{r, warning=FALSE, message=FALSE}
CrossTable(Data$Parent, Data$emCondition, format = 'SPSS', chisq = T)
```

## Correlations with Order
```{r, warning=FALSE, message=FALSE}
CrossTable(Data$Parent, Data$Order, format = 'SPSS', chisq = T)
```

## Correlations with Trust
```{r, warning=FALSE, message=FALSE}
Data %>% 
  group_by(Parent) %>% 
  summarise(Mean = round(mean(Trust), 2),
            SD   = round(sd(Trust), 2))

varTest <- var.test(Trust ~ Parent, data = Data)
trueVarTest <- ifelse(varTest$p.value > 0.05, TRUE, FALSE)
Model <- t.test(Trust ~ Parent, var.equal = trueVarTest, data = Data)
Model
```

## Correlations with Trust
```{r, warning=FALSE, message=FALSE}
Data %>% 
  group_by(Parent) %>% 
  summarise(Mean = round(mean(Trust), 2),
            SD   = round(sd(Trust), 2))

varTest <- var.test(Trust ~ Parent, data = Data)
trueVarTest <- ifelse(varTest$p.value > 0.05, TRUE, FALSE)
Model <- t.test(Trust ~ Parent, var.equal = trueVarTest, data = Data)
Model
```

# Religion
## Descriptive statistics
```{r, warning=FALSE, message=FALSE}
table(Data$Religion)
round(100 * table(Data$Religion) / nrow(Data), 2)
```

## Correlations with emCondition
```{r, warning=FALSE, message=FALSE}
CrossTable(Data$Religion, Data$emCondition, format = 'SPSS', chisq = T)
```

## Correlations with Order
```{r, warning=FALSE, message=FALSE}
CrossTable(Data$Religion, Data$Order, format = 'SPSS', chisq = T)
```

## Correlations with Trust
```{r, warning=FALSE, message=FALSE}
Data %>% 
  group_by(Religion) %>% 
  summarise(Mean = round(mean(Trust), 2),
            SD   = round(sd(Trust), 2))

varTest <- var.test(Trust ~ Religion, data = Data)
trueVarTest <- ifelse(varTest$p.value > 0.05, TRUE, FALSE)
Model <- t.test(Trust ~ Religion, var.equal = trueVarTest, data = Data)
Model
```

## Correlations with Trust
```{r, warning=FALSE, message=FALSE}
Data %>% 
  group_by(Religion) %>% 
  summarise(Mean = round(mean(Trust), 2),
            SD   = round(sd(Trust), 2))

varTest <- var.test(Trust ~ Religion, data = Data)
trueVarTest <- ifelse(varTest$p.value > 0.05, TRUE, FALSE)
Model <- t.test(Trust ~ Religion, var.equal = trueVarTest, data = Data)
Model
```

# religionAffiliation
## Descriptive statistics
```{r, warning=FALSE, message=FALSE}
table(Data$religionAffilation)
round(100 * table(Data$religionAffilation) / nrow(Data), 2)
```

## Correlations with emCondition
```{r, warning=FALSE, message=FALSE}
CrossTable(Data$religionAffiliation, Data$emCondition, format = 'SPSS', chisq = T)
```

## Correlations with Order
```{r, warning=FALSE, message=FALSE}
CrossTable(Data$religionAffiliation, Data$Order, format = 'SPSS', chisq = T)
```

## Correlations with Amount
```{r, warning=FALSE, message=FALSE}
Data %>% 
  group_by(religionAffiliation) %>% 
  summarise(Mean = round(mean(Amount), 2),
            SD   = round(sd(Amount), 2))

Leven <- leveneTest(Data$Amount ~ Data$religionAffiliation)  # car packages
trueVarTest <- ifelse(varTest$p.value > 0.05, TRUE, FALSE)
Model <- aov(Amount ~ religionAffiliation, var.equal = trueVarTest, data = Data)
Anova(Model, type = 'III', white.adjust = trueVarTest)
```

## Correlations with Trust
```{r, warning=FALSE, message=FALSE}
Data %>% 
  group_by(religionAffiliation) %>% 
  summarise(Mean = round(mean(Trust), 2),
            SD   = round(sd(Trust), 2))

Leven <- leveneTest(Data$Trust ~ Data$religionAffiliation)  # car packages
trueVarTest <- ifelse(varTest$p.value > 0.05, TRUE, FALSE)
Model <- aov(Trust ~ religionAffiliation, var.equal = trueVarTest, data = Data)
Anova(Model, type = 'III', white.adjust = trueVarTest)
```


# Education
## Descriptive statistics
```{r, warning=FALSE, message=FALSE}
table(Data$Education)
round(100 * table(Data$Education) / nrow(Data), 2)
```

## Correlations with emCondition
```{r, warning=FALSE, message=FALSE}
CrossTable(Data$Education, Data$emCondition, format = 'SPSS', chisq = T)
```

## Correlations with Order
```{r, warning=FALSE, message=FALSE}
CrossTable(Data$Education, Data$Order, format = 'SPSS', chisq = T)
```

## Correlations with Amount
```{r, warning=FALSE, message=FALSE}
Data %>% 
  group_by(Education) %>% 
  summarise(Mean = round(mean(Amount), 2),
            SD   = round(sd(Amount), 2))

Leven <- leveneTest(Data$Amount ~ Data$Education)  # car packages
trueVarTest <- ifelse(varTest$p.value > 0.05, TRUE, FALSE)
Model <- aov(Amount ~ Education, var.equal = trueVarTest, data = Data)
Anova(Model, type = 'III', white.adjust = trueVarTest)
```

## Correlations with Trust
```{r, warning=FALSE, message=FALSE}
Data %>% 
  group_by(Education) %>% 
  summarise(Mean = round(mean(Trust), 2),
            SD   = round(sd(Trust), 2))

Leven <- leveneTest(Data$Trust ~ Data$Education)  # car packages
trueVarTest <- ifelse(varTest$p.value > 0.05, TRUE, FALSE)
Model <- aov(Trust ~ Education, var.equal = trueVarTest, data = Data)
Anova(Model, type = 'III', white.adjust = trueVarTest)
```


# Socioeconomic
## Descriptive statistics
```{r, warning=FALSE, message=FALSE}
table(Data$Socioeconomic)
round(100 * table(Data$Socioeconomic) / nrow(Data), 2)
```

## Correlations with emCondition
```{r, warning=FALSE, message=FALSE}
CrossTable(Data$Socioeconomic, Data$emCondition, format = 'SPSS', chisq = T)
```

## Correlations with Order
```{r, warning=FALSE, message=FALSE}
CrossTable(Data$Socioeconomic, Data$Order, format = 'SPSS', chisq = T)
```

## Correlations with Amount
```{r, warning=FALSE, message=FALSE}
Data %>% 
  group_by(Socioeconomic) %>% 
  summarise(Mean = round(mean(Amount), 2),
            SD   = round(sd(Amount), 2))

Leven <- leveneTest(Data$Amount ~ Data$Socioeconomic)  # car packages
trueVarTest <- ifelse(varTest$p.value > 0.05, TRUE, FALSE)
Model <- aov(Amount ~ Socioeconomic, var.equal = trueVarTest, data = Data)
Anova(Model, type = 'III', white.adjust = trueVarTest)
```

## Correlations with Trust
```{r, warning=FALSE, message=FALSE}
Data %>% 
  group_by(Socioeconomic) %>% 
  summarise(Mean = round(mean(Trust), 2),
            SD   = round(sd(Trust), 2))

Leven <- leveneTest(Data$Trust ~ Data$Socioeconomic)  # car packages
trueVarTest <- ifelse(varTest$p.value > 0.05, TRUE, FALSE)
Model <- aov(Trust ~ Socioeconomic, var.equal = trueVarTest, data = Data)
Anova(Model, type = 'III', white.adjust = trueVarTest)
```

# Political
## Descriptive statistics
```{r, warning=FALSE, message=FALSE}
table(Data$Political)
round(100 * table(Data$Political) / nrow(Data), 2)
```

## Correlations with emCondition
```{r, warning=FALSE, message=FALSE}
CrossTable(Data$Political, Data$emCondition, format = 'SPSS', chisq = T)
```

## Correlations with Order
```{r, warning=FALSE, message=FALSE}
CrossTable(Data$Political, Data$Order, format = 'SPSS', chisq = T)
```

## Correlations with Amount
```{r, warning=FALSE, message=FALSE}
Data %>% 
  group_by(Political) %>% 
  summarise(Mean = round(mean(Amount), 2),
            SD   = round(sd(Amount), 2))

Leven <- leveneTest(Data$Amount ~ Data$Political)  # car packages
trueVarTest <- ifelse(varTest$p.value > 0.05, TRUE, FALSE)
Model <- aov(Amount ~ Political, var.equal = trueVarTest, data = Data)
Anova(Model, type = 'III', white.adjust = trueVarTest)
```

## Correlations with Trust
```{r, warning=FALSE, message=FALSE}
Data %>% 
  group_by(Political) %>% 
  summarise(Mean = round(mean(Trust), 2),
            SD   = round(sd(Trust), 2))

Leven <- leveneTest(Data$Trust ~ Data$Political)  # car packages
trueVarTest <- ifelse(varTest$p.value > 0.05, TRUE, FALSE)
Model <- aov(Trust ~ Political, var.equal = trueVarTest, data = Data)
Anova(Model, type = 'III', white.adjust = trueVarTest)
```

