---
title: "Report"
author: "Tom Mushkat"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    code_folding: hide
    df_print: kable
    results: hide
    theme: readable
    toc: TRUE
    toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, warning=FALSE, message=FALSE}
pacman::p_load(tidyverse, here, skimr, anytime, car, effectsize, gmodels, apaTables, psych, rcompanion, ResourceSelection, lmtest, faraway, estimatr, tidymodels, hdm)

Data <- read_csv(here('Data/cleanDataUpdated.csv'))

Data$emCondition <- as.factor(Data$emCondition)
levels(Data$emCondition)
contrasts(Data$emCondition)
# Data %>% 
#   group_by(emCondition) %>% 
#   summarise(m = mean(Trust)) 
# summary(lm(Trust ~ emCondition, data = Data))

Data$emCondition <- ordered(Data$emCondition, levels = c('No', 'Single', 'Many'))
# Data %>% 
#   group_by(emCondition) %>% 
#   summarise(m = mean(Trust)) 

Single <- c(0, 1, 0)
Many <- c(0, 0, 1)
contrasts(Data$emCondition) <- cbind(Single, Many)
# summary(lm(Trust ~ emCondition, data = Data))

# newData <- Data %>% filter(understandPurpse != 'didNotUnderstand')
# nrow(newData)

Data <- Data %>% 
  filter(understandPurpse == 'didNotUnderstand')

```

# Correlation between the DVs

We can see a medium size positive correlation between the Trust in Player B, and the money s.he recived.
```{r, warning=FALSE, message=FALSE}
cor.test(Data$Amount, Data$Trust)
```

# Controls 
## Only controls
### Correlation table
There are strong positive correlations between all the controls:

(1) Frequency of emoji use

(2) Attitudes towards emojis

(3) Motive to use emojis

(4) How much the massage influence (negative-positive)

```{r, warning=FALSE, message=FALSE}
apa.cor.table(as.matrix(cbind(emojiUse = Data$emojiUse, Attitudes = Data$Attitudes, Motives = Data$Motives, influencedFactors = Data$influencedFactors)))
```

### Difference by understanding the EXP purpose

The participants who understood the manipulation (indicated that they understood that the manipulation was about emojis when Player B sent the message) were not influenced by the message (marginally) in comparison with the participants that did not understand the purpose.

```{r, warning=FALSE, message=FALSE}
Data %>% 
  group_by(understandPurpse ) %>% 
  summarise(Mean = round(mean(influencedFactors), 2),
            SD   = round(sd(influencedFactors), 2),
            N = length(influencedFactors))

varTest <- var.test(influencedFactors ~ understandPurpse , data = Data)
trueVarTest <- ifelse(varTest$p.value > 0.05, TRUE, FALSE)
Model <- t.test(influencedFactors ~ understandPurpse , var.equal = trueVarTest, data = Data)
Model

effectsize(Model)

boxplot(Data$influencedFactors ~ Data$understandPurpse ,
  ylab = "Influenced by Player B negative-positive",
  main = 'Understand Purpse '
)
```

## Difference at the controls by gender

Females used emoji more often, and had better attitudes and motives towards emojis in comparison with males. However, females were not influenced more than males by Player B. Moreover, higher frequency of females understand the EXP purpose in comparison with males.

### Frequency * Gender
```{r, warning=FALSE, message=FALSE}
Data %>% 
  group_by(mf) %>% 
  summarise(Mean = round(mean(emojiUse), 2),
            SD   = round(sd(emojiUse), 2),
            N = length(emojiUse))

varTest <- var.test(emojiUse ~ mf , data = Data)
trueVarTest <- ifelse(varTest$p.value > 0.05, TRUE, FALSE)
Model <- t.test(emojiUse ~ mf , var.equal = trueVarTest, data = Data)
Model

effectsize(Model)

boxplot( Data$emojiUse ~ Data$mf ,
  ylab = "Frequency",
  main = 'Frequency * Gender '
)
```

### Attitudes * Gender

```{r, warning=FALSE, message=FALSE}
Data %>% 
  group_by(mf) %>% 
  summarise(Mean = round(mean(Attitudes), 2),
            SD   = round(sd(Attitudes), 2),
            N = length(Attitudes))

varTest <- var.test(Attitudes ~ mf , data = Data)
trueVarTest <- ifelse(varTest$p.value > 0.05, TRUE, FALSE)
Model <- t.test(Attitudes ~ mf , var.equal = trueVarTest, data = Data)
Model

effectsize(Model)

boxplot(Data$Attitudes ~ Data$mf ,
  ylab = "Attitudes",
  main = 'Attitudes * Gender'
)
```

### Motives * Gender

```{r, warning=FALSE, message=FALSE}
Data %>% 
  group_by(mf) %>% 
  summarise(Mean = round(mean(Motives), 2),
            SD   = round(sd(Motives), 2),
            N = length(Motives))

varTest <- var.test(Motives ~ mf , data = Data)
trueVarTest <- ifelse(varTest$p.value > 0.05, TRUE, FALSE)
Model <- t.test(Motives ~ mf , var.equal = trueVarTest, data = Data)
Model

effectsize(Model)

boxplot(Data$Motives ~ Data$mf ,
  ylab = "Motives",
  main = 'Motives * Gender'
)
```

### Influenced * Gender

```{r, warning=FALSE, message=FALSE}

Data %>% 
  group_by(mf) %>% 
  summarise(Mean = round(mean(influencedFactors), 2),
            SD   = round(sd(influencedFactors), 2),
            N = length(influencedFactors))

varTest <- var.test(influencedFactors ~ mf , data = Data)
trueVarTest <- ifelse(varTest$p.value > 0.05, TRUE, FALSE)
Model <- t.test(influencedFactors ~ mf , var.equal = trueVarTest, data = Data)
Model
```

### Understand Purpse * Gender

```{r, warning=FALSE, message=FALSE}
CrossTable(Data$understandPurpse, Data$mf, chisq = T, format = 'SPSS')
Model <- chisq.test(Data$understandPurpse, Data$mf, correct = FALSE)
effectsize(Model, type = 'phi')
```

# Correlations of the DV with Controls and Gender

We can see strong and positive correlations between the continuous controls and the Trust in player B. However, for the Amount given, there was a positive correlation only with degree of influence by Player B.

We can see that males trusted more in Player B and gave more money in comparison with females.
We can see that there are no significant difference at the DVs by understanding the manipulation. However, the size effects are large and indicate that the participants who understand the manipulation trusted lass and gave less money. 

## (1) Correlation tables between the continuous controls and Amount
## (2) Correlation tables between the continuous controls and Trust

```{r, warning=FALSE, message=FALSE}
apa.cor.table(as.matrix(cbind(Amount = Data$Amount, emojiUse = Data$emojiUse, Attitudes = Data$Attitudes, Motives = Data$Motives, Influece = Data$influencedFactors)))


apa.cor.table(as.matrix(cbind(Trust = Data$Trust, emojiUse = Data$emojiUse, Attitudes = Data$Attitudes, Motives = Data$Motives, Influece = Data$influencedFactors)))
```

## Amount * Gender

```{r, warning=FALSE, message=FALSE}
Data %>% 
  group_by(mf) %>% 
  summarise(Mean = round(mean(Amount), 2),
            SD   = round(sd(Amount), 2),
            N = length(Amount))

varTest <- var.test(Amount ~ mf , data = Data)
trueVarTest <- ifelse(varTest$p.value > 0.05, TRUE, FALSE)
Model <- t.test(Amount ~ mf , var.equal = trueVarTest, data = Data)
Model


effectsize(Model)

boxplot(Data$Amount ~ Data$mf ,
  ylab = "Amount",
  main = 'Amount * Gender'
)
```

## Trust * Gender
```{r, warning=FALSE, message=FALSE}
Data %>% 
  group_by(mf) %>% 
  summarise(Mean = round(mean(Trust), 2),
            SD   = round(sd(Trust), 2),
            N = length(Trust))

varTest <- var.test(Trust ~ mf , data = Data)
trueVarTest <- ifelse(varTest$p.value > 0.05, TRUE, FALSE)
Model <- t.test(Trust ~ mf , var.equal = trueVarTest, data = Data)
Model


effectsize(Model)

boxplot(Data$Trust ~ Data$mf ,
  ylab = "Trust",
  main = 'Trust * Gender'
)
```

## Amount * Understand Purpose

```{r, warning=FALSE, message=FALSE}
Data %>% 
  group_by(understandPurpse) %>% 
  summarise(Mean = round(mean(Amount), 2),
            SD   = round(sd(Amount), 2),
            N = length(Amount))

varTest <- var.test(Amount ~ understandPurpse , data = Data)
trueVarTest <- ifelse(varTest$p.value > 0.05, TRUE, FALSE)
Model <- t.test(Amount ~ understandPurpse , var.equal = trueVarTest, data = Data)
Model


effectsize(Model)

boxplot(Data$Amount ~ Data$understandPurpse ,
  ylab = "Amount",
  main = 'Amount * Understand Purpse'
)
```

## Trust * Understand Purpose

```{r, warning=FALSE, message=FALSE}
Data %>% 
  group_by(understandPurpse) %>% 
  summarise(Mean = round(mean(Trust), 2),
            SD   = round(sd(Trust), 2),
            N = length(Trust))

varTest <- var.test(Trust ~ understandPurpse , data = Data)
trueVarTest <- ifelse(varTest$p.value > 0.05, TRUE, FALSE)
Model <- t.test(Trust ~ understandPurpse , var.equal = trueVarTest, data = Data)
Model


effectsize(Model)

boxplot(Data$Trust ~ Data$understandPurpse ,
  ylab = "Trust",
  main = 'Trust * Understand Purpse'
)
```



# participatns who indicated to be influence bt Player B

## Influenced by B * Understand Purpose

We can see that the participants who indicated to be influenced b Player B were influenced more positively by Player B, gave more money but did not trusted him.
They also did not understood the study's purpose, and there was no correlation with gender. 

## Understand Purpse * Understand Purpose

```{r, warning=FALSE, message=FALSE}
CrossTable(Data$influencedByB, Data$understandPurpse, chisq = T, format = 'SPSS')
```

## Gender * influenced By B
```{r, warning=FALSE, message=FALSE}
CrossTable(Data$influencedByB, Data$mf, chisq = T, format = 'SPSS')
```

## Influenced * influenced By B
```{r, warning=FALSE, message=FALSE}

Data %>% 
  group_by(influencedByB) %>% 
  summarise(Mean = round(mean(influencedFactors), 2),
            SD   = round(sd(influencedFactors), 2),
            N = length(influencedFactors))

varTest <- var.test(influencedFactors ~ influencedByB , data = Data)
trueVarTest <- ifelse(varTest$p.value > 0.05, TRUE, FALSE)
Model <- t.test(influencedFactors ~ influencedByB , var.equal = trueVarTest, data = Data)
Model

boxplot(Data$influencedFactors ~ Data$influencedByB ,
  ylab = "Influenced positive negative",
  main = 'Influenced * influenced By B'
)
```

## Amount * influenced By B
```{r, warning=FALSE, message=FALSE}

Data %>% 
  group_by(influencedByB) %>% 
  summarise(Mean = round(mean(Amount), 2),
            SD   = round(sd(Amount), 2),
            N = length(Amount))

varTest <- var.test(Amount ~ influencedByB , data = Data)
trueVarTest <- ifelse(varTest$p.value > 0.05, TRUE, FALSE)
Model <- t.test(Amount ~ influencedByB , var.equal = trueVarTest, data = Data)
Model

boxplot(Data$Amount ~ Data$influencedByB ,
  ylab = "Amount",
  main = 'Amount * influencedByB'
)
```


## Trust * influenced By B
```{r, warning=FALSE, message=FALSE}

Data %>% 
  group_by(influencedByB) %>% 
  summarise(Mean = round(mean(Trust), 2),
            SD   = round(sd(Trust), 2),
            N = length(Trust))

varTest <- var.test(Trust ~ influencedByB , data = Data)
trueVarTest <- ifelse(varTest$p.value > 0.05, TRUE, FALSE)
Model <- t.test(Trust ~ influencedByB , var.equal = trueVarTest, data = Data)
Model
```












# One-ways
```{r, warning=FALSE, message=FALSE}
CrossTable(Data$influencedByB, Data$understandPurpse, chisq = T, format = 'SPSS')

Data$emConditionOneWayAmount <- as.factor(Data$emCondition)
contrasts(Data$emConditionOneWayAmount)
EMvsNoEM <- c(0, 1, 0)
ManyVSSingle <- c(1, 0, 0)
contrasts(Data$emConditionOneWayAmount) <- cbind(EMvsNoEM, ManyVSSingle)

Data$emConditionOneWayTrust <- as.factor(Data$emCondition)
contrasts(Data$emConditionOneWayTrust)
EMvsNoEM <- c(0, 1, 0)
ManyVSSingle <- c(1, 0, 0)
contrasts(Data$emConditionOneWayTrust) <- cbind(EMvsNoEM, ManyVSSingle)

contrasts(Data$emConditionOneWayAmount)
contrasts(Data$emConditionOneWayTrust)
```

## Amount
```{r, warning=FALSE, message=FALSE}
Data %>% 
  mutate(emCondition = ordered(emCondition, levels = c('No', 'Single', 'Many'))) %>% 
  # filter(Order == 'amountFirst') %>% 
  group_by(emCondition) %>% 
  summarise(Mean = round(mean(Amount), 2),
            SD   = round(sd(Amount), 2),
            N = length(Amount))

Leven <- leveneTest(Data$Amount ~ Data$emConditionOneWayAmount)  # car packages
trueVarTest <- ifelse(Leven$`Pr(>F)`[1] < 0.05, TRUE, FALSE)
Model <- aov(Amount ~ emConditionOneWayAmount, data = Data)
Anova(Model, type = 'III', white.adjust = trueVarTest)

Data %>% 
  # filter(Order == 'questionFirst') %>% 
        mutate(emCondition = ordered(emCondition, levels = c('No', 'Single', 'Many'))) %>% 
  ggplot(aes(x = emCondition, y = Amount, fill = emCondition)) + 
    # geom_bar(stat = 'summary', position = position_dodge()) +
  geom_boxplot(color = 'purple', alpha = 2) + 
      geom_violin(alpha = 0.1) +
  scale_fill_manual(values = c('darkgrey', 'lightgrey', 'lightgreen')) +
  geom_jitter(aes(x = emCondition, y = Amount, fill = emCondition), color = 'blue') + 
    stat_summary(fun.data = mean_sdl, fun.args = list(mult = 1), 
               geom = "errorbar", color = "red", width = 0.2) +
    stat_summary(fun.y = mean, geom = "point", color = "red") +
    theme_classic() + ylab('Money') + xlab('Emoji level') + 
    ggtitle('One-Way ANOVA bar plot: Money by Emoji') +
  theme(plot.title = element_text(hjust = 0.5))

```

## Trust
```{r, warning=FALSE, message=FALSE}
Data %>% 
  # filter(Order == 'questionFirst') %>% 
    mutate(emCondition = ordered(emCondition, levels = c('No', 'Single', 'Many'))) %>% 
  group_by(emCondition) %>% 
  summarise(Mean = round(mean(Trust), 2),
            SD   = round(sd(Trust), 2),
            N = length(Trust))

Leven1 <- leveneTest(Data$Trust ~ Data$emConditionOneWayTrust)  # car packages

trueVarTest <- ifelse(Leven1$`Pr(>F)`[1] < 0.05, TRUE, FALSE)
Model <- aov(Trust ~ emConditionOneWayTrust, data = Data)
Anova(Model, type = 'III', white.adjust = trueVarTest)


Data %>% 
  # filter(Order == 'questionFirst') %>% 
  # filter(mf == 'Female') %>% 
    mutate(emCondition = ordered(emCondition, levels = c('No', 'Single', 'Many'))) %>% 
  ggplot(aes(x = emCondition, y = Trust, fill = emCondition)) + 
    # geom_bar(stat = 'summary', position = position_dodge()) +
  geom_boxplot(color = 'purple', alpha = 2) + 
      geom_violin(alpha = 0.1) +
  scale_fill_manual(values = c('darkgrey', 'lightgrey', 'lightgreen')) +
  geom_jitter(aes(x = emCondition, y = Trust, fill = emCondition), color = 'blue') + 
    stat_summary(fun.data = mean_sdl, fun.args = list(mult = 1), 
               geom = "errorbar", color = "red", width = 0.2) +
    stat_summary(fun.y = mean, geom = "point", color = "red") +
    theme_classic() + ylab('Trust') + xlab('Emoji level') + 
    ggtitle('One-Way ANOVA bar plot: Trust by Emoji') +
  theme(plot.title = element_text(hjust = 0.5))
```


# Two-way influence * emoji no order
## Amount
```{r, warning=FALSE, message=FALSE}
Data %>% 
  group_by(emCondition, influencedByB) %>% 
  summarise(Mean = round(mean(Amount), 2),
            SD   = round(sd(Amount), 2),
            Max = max(Amount),
            Min = min(Amount),
            N = length(Amount))


Leven1 <- leveneTest(Data$Amount ~ Data$emCondition)  # car packages
Leven2 <- leveneTest(Data$Amount ~ Data$influencedByB)  # car packages
Leven3 <- leveneTest(Data$Amount ~ Data$emCondition:Data$influencedByB)  # car packages
Leven4 <- leveneTest(Data$Amount ~ Data$mf)  # car packages
# Leven5 <- leveneTest(Data$Amount ~ Data$Secular)  # car packages


trueVarTest <- ifelse(Leven1$`Pr(>F)`[1] < 0.05 | Leven2$`Pr(>F)`[1] < 0.05 | Leven3$`Pr(>F)`[1] < 0.05 | Leven4$`Pr(>F)`[1] < 0.05, TRUE, FALSE)
Model <- aov(Amount ~ emCondition * influencedByB + mf, data = Data)
Anova(Model, type = 'III', white.adjust = trueVarTest)


Data %>% 
      mutate(emCondition = ordered(emCondition, levels = c('No', 'Single', 'Many'))) %>% 
  ggplot(aes(x = emCondition, y = Amount, fill = influencedByB)) + 
    # geom_bar(stat = 'summary', position = position_dodge()) +
    geom_boxplot(aes(color = influencedByB), alpha = 0.1, position = position_dodge(0.8), size = 1) + 
      geom_violin(alpha = 0.1, position = position_dodge(0.8)) +
  scale_fill_manual(values = c('darkgrey', 'lightgrey')) +
  # geom_jitter(aes(x = emCondition, y = Amount, fill = Order), color = 'blue') + 
     stat_summary(fun.data = mean_sdl, fun.args = list(mult = 1), 
               geom = "errorbar", color = "purple", width = 0.2, position = position_dodge(0.8)) +
    stat_summary(fun.y = mean, geom = "point", color = "purple", position = position_dodge(0.8), size = 2) +
    theme_classic() + ylab('Money') + xlab('Emoji level') + 
    ggtitle('Two-Way ANOVA bar plot: Money by Emoji') +
  theme(plot.title = element_text(hjust = 0.5)) + 
  facet_grid(~mf)


Data %>% 
      mutate(emCondition = ordered(emCondition, levels = c('No', 'Single', 'Many'))) %>% 
  ggplot(aes(x = emCondition, y = Amount, fill = influencedByB)) + 
    stat_summary(aes(group = influencedByB, color = influencedByB), fun.y = "mean", geom = "line", 
                 position = position_dodge(0.2)) + 
    stat_summary(fun.y = "mean", geom = "point", aes(color = influencedByB), 
                 position = position_dodge(0.2)) + 
    stat_summary(fun.data = mean_sdl, geom = "errorbar", aes(color = influencedByB),
                 position = position_dodge(0.2), width = 0.2) + 
    theme_classic() + ylab('Money') + xlab('Emoji level') + 
    ggtitle('Two-Way ANOVA: Money by Emoji * influencedByB') + theme(plot.title = element_text(hjust = 0.5)) 
  facet_grid(~mf)
  
CrossTable(Data$everPlayed, Data$influencedByB, chisq = T, format = 'SPSS')


```

## Trust
```{r, warning=FALSE, message=FALSE}
Data %>% 
  group_by(mf, influencedByB) %>% 
  summarise(Mean = round(mean(Trust), 2),
            SD   = round(sd(Trust), 2),
            Max = max(Trust),
            Min = min(Trust),
            N = length(Trust))



Leven1 <- leveneTest(Data$Trust ~ Data$emCondition)  # car packages
Leven2 <- leveneTest(Data$Trust ~ Data$influencedByB)  # car packages
Leven3 <- leveneTest(Data$Trust ~ Data$emCondition:Data$influencedByB)  # car packages
Leven4 <- leveneTest(Data$Trust ~ Data$mf)  
Leven5 <- leveneTest(Data$Trust ~ Data$Secular)  


trueVarTest <- ifelse(Leven1$`Pr(>F)`[1] < 0.05 | Leven2$`Pr(>F)`[1] < 0.05 | Leven3$`Pr(>F)`[1] < 0.05 | Leven4$`Pr(>F)`[1] < 0.05 | Leven5$`Pr(>F)`[1] < 0.05, TRUE, FALSE)
Model <- aov(Trust ~ emCondition * influencedByB + mf + Secular + Motives, data = Data)
Anova(Model, type = 'III', white.adjust = trueVarTest)



Data %>% 
      mutate(emCondition = ordered(emCondition, levels = c('No', 'Single', 'Many'))) %>% 
  ggplot(aes(x = emCondition, y = Trust, fill = influencedByB)) + 
    # geom_bar(stat = 'summary', position = position_dodge()) +
    geom_boxplot(aes(color = influencedByB), alpha = 0.1, position = position_dodge(0.8), size = 1) + 
      geom_violin(alpha = 0.1, position = position_dodge(0.8)) +
  scale_fill_manual(values = c('darkgrey', 'lightgrey')) +
  # geom_jitter(aes(x = emCondition, y = Amount, fill = Order), color = 'blue') + 
     stat_summary(fun.data = mean_sdl, fun.args = list(mult = 1), 
               geom = "errorbar", color = "purple", width = 0.2, position = position_dodge(0.8)) +
    stat_summary(fun.y = mean, geom = "point", color = "purple", position = position_dodge(0.8), size = 2) +
    theme_classic() + ylab('Trust') + xlab('Emoji level') + 
    ggtitle('Two-Way ANOVA bar plot: Trust by Emoji') +
  theme(plot.title = element_text(hjust = 0.5)) 
  # facet_grid(~mf)



Data %>% 
      mutate(emCondition = ordered(emCondition, levels = c('No', 'Single', 'Many'))) %>% 
  ggplot(aes(x = emCondition, y = Trust, fill = influencedByB)) + 
    stat_summary(aes(group = influencedByB, color = influencedByB), fun.y = "mean", geom = "line", 
                 position = position_dodge(0.2)) + 
    stat_summary(fun.y = "mean", geom = "point", aes(color = influencedByB), 
                 position = position_dodge(0.2)) + 
    stat_summary(fun.data = mean_sdl, geom = "errorbar", aes(color = influencedByB),
                 position = position_dodge(0.2), width = 0.2) + 
    theme_classic() + ylab('Trust') + xlab('Emoji level') + 
    ggtitle('Two-Way ANOVA: Trust by Emoji * influencedByB') + theme(plot.title = element_text(hjust = 0.5))  
    # facet_grid(~mf)

```

# Logistic regression for predicting the Amount

## Performing the model
```{r, warning=FALSE, message=FALSE}
Model <- kmeans(x = Data$Amount, centers = 2)
Model
Data$clusters <- Model$cluster
Data$clusters <- ifelse(Data$clusters == 2, 1, 0)
Data$clusters <- as.factor(Data$clusters)
```

This is the distribution of the money that was sent to Player B.
We can see that some of the participants sent the max amount, and some, about 5 cents.

Therefore using K-Means method I split the data into two groups. and performed logistic regression for predicting the new clusters using the emoji condition.
The regression was conducted while controlling the Gender.
```{r, warning=FALSE, message=FALSE}
hist(Data$Amount)
```

# Performing logistic regression for predicting 

The model was significant $(X^2(3) = 11.42, p < .01)$ while explaining 5.34% of the total variance in the Trust in Player B.
The model is well-fit to data $(X^2(8) = 0.64, p = .99)$ while classifying about 60.5% of total observations, with sensitivity of 68.82% and specificity of 43.44%.
After controlling the participants' gender, the model showed a negative correlation between the use of multiple emoji and money sending ($OR = 0.50, CI[0.28, 0.91], p = .02)$. Meaning, the participants in the multiple emoji condition, sent less money to Player B in comparison with the participants in the Single emoji condition.
The summary of the model and the Odds ratio with the CI are presented below.

```{r, warning=FALSE, message=FALSE}
regLog1 <- glm(clusters ~ emCondition + mf + influencedFactors, family = binomial('logit'), data = Data)
summary(regLog1)

Data %>%
  ggplot(aes(x = emCondition, y = Clusters)) +
  geom_bar(aes(y = (..count..) / sum(..count..), fill = emCondition)) + 
          scale_y_continuous(labels = scales::percent) +
   geom_text(aes( label = scales::percent(..prop..),
                   y = ..prop.. ), stat = "count", vjust = -.5) +
  ylab("Relative frequencies") + theme_classic() + 
  scale_y_continuous(labels = scales::percent) 
  # facet_grid(~clusters ) +
  ylim(0, 0.50)
  

  CrossTable(Data$clusters, Data$emCondition, chisq = T, format = 'SPSS')
```

## Odss ratio
Extracting the odds ratio
```{r, warning=FALSE, message=FALSE}
ORCI <- round(exp(cbind(coef(regLog1), confint(regLog1))), 2) 
ORCI
```

# LM for predicting the Trust
Linear regression was performed for predicting the Trust in Player B.
The regression was performed while controlling gender, religiously, Motives, Attitudes and emoji Use (No multicollinearity was found).
The model was significant $(F(7) = 3.75, p < .01)$ while explaining 6.4% of the total variance in the Trust in Player B.
After controlling the control variables, there was found no correlations between 
## Performing linear regression

```{r, warning=FALSE, message=FALSE}
Model <- lm(Trust ~ emCondition + mf + Secular + Motives + Attitudes + emojiUse + influencedFactors, data = Data) 
vif(Model)
varTest <- bptest(Model)    # lmtest package
regType <- ifelse(varTest$p.value < 0.05, 'HC2', 'classical')

Model <- lm_robust(Trust ~ emCondition + mf + Secular + Motives + Attitudes + emojiUse + influencedFactors, se_type =  regType, data = Data)

summary(Model)
```

### Standerlized beta coeff 
```{r, warning=FALSE, message=FALSE}
scalednewData <- Data %>% 
  mutate(Motives = scale(Motives),
         Attitudes = scale(Attitudes),
         emojiUse = scale(emojiUse),
         Trust = scale(Trust))

Model1 <- lm_robust(Trust ~ emCondition + mf + Secular + Motives + Attitudes + emojiUse + influencedFactors, se_type = regType, data = scalednewData) # estimatr package
summary(Model1)
```